How has the Brazilian Amazon been constructed as a problem? The economy, the environment, the people, and the nation in the presidential speeches since 1985

### 2022-05-11 Draft_April_2022/Full_draft_20220401.rmd
Harmonized scales for figure 4 as well

```{r Figure 5: pure types in time by location, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE, out.width= "50%"}
pure_types_time_location <- ama_mx %>%
  count(mx_cat2, mx_cat, year, location_cat) %>%
  group_by(year) %>%
  mutate(perc = n / sum(n)) %>% 
  filter(mx_cat2 == "Pure-types") %>%
  filter(location_cat != "Non Identified") %>%
  ggplot(aes(x=as.numeric(year), y=perc, color=mx_cat)) +
  geom_smooth(aes(color=mx_cat), se=FALSE, size=.5) +
  scale_y_continuous(labels = percent_format(accuracy=1)) +
  labs(x = "", y = "", title ="Share of each pure type in time by location",
       subtitle = "Sample composed by 1895 Amazonian statements in presidential speeches since 1985",
       caption = "") +
  theme(panel.background = element_rect("white", "black", .5, "solid"),
        panel.grid.major = element_line(color = "grey", size = 0.3, linetype = "solid"),
        axis.text = element_text(color = "black", size = 10),
        title = element_text(color = "black", size = 10, face = "bold"),
        legend.title = element_blank(),
        plot.subtitle = element_text(color = "black", size = 9, face = "plain"),
        legend.position = "bottom") +
  facet_wrap(~location_cat, scales= "free_y", ncol=2)
pure_types_time_location
```

>>>>

```{r Figure 5: pure types in time by location, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE, out.width= "50%"}
pure_types_time_location <- ama_mx %>%
  count(mx_cat2, mx_cat, year, location_cat) %>%
  group_by(year) %>%
  mutate(perc = n / sum(n)) %>% 
  filter(mx_cat2 == "Pure-types") %>%
  filter(location_cat != "Non Identified") %>%
  ggplot(aes(x=as.numeric(year), y=perc, color=mx_cat)) +
  geom_smooth(aes(color=mx_cat), se=FALSE, size=.5) +
  scale_y_continuous(labels = percent_format(accuracy=1)) +
  labs(x = "", y = "", title ="Share of each pure type in time by location",
       subtitle = "Sample composed by 1895 Amazonian statements in presidential speeches since 1985",
       caption = "") +
  theme(panel.background = element_rect("white", "black", .5, "solid"),
        panel.grid.major = element_line(color = "grey", size = 0.3, linetype = "solid"),
        axis.text = element_text(color = "black", size = 10),
        title = element_text(color = "black", size = 10, face = "bold"),
        legend.title = element_blank(),
        plot.subtitle = element_text(color = "black", size = 9, face = "plain"),
        legend.position = "bottom") +
  facet_wrap(~location_cat, ncol=2)
pure_types_time_location
```
